%# -*- coding: utf-8-unix -*-
%%==================================================
%% abstract.tex for SJTU Master Thesis
%%==================================================

\begin{abstract}

近年来，O2O(Online To Offline)商务平台在居民的消费生活中作用越来越重要。然而，在名誉和利益的驱动下，有一部分人试图使用网络诈骗的方式，例如发布水军评论和虚假内容，恶意操作线上市场。这种行为极大地危害了线上市场的环境，应当被立即侦测并驱除。而且，比起简单的僵尸网络机器水军，那些人工水军的隐蔽性和危害性更大。虽然目前在网络水军检测领域已经存在各种成熟的方法，但是这些知名的方法都几乎忽略了地理位置因素。我们的调查显示地理位置因素可以很好地反映水军用户和普通用户之间的差异。在这篇论文中，我们分析了评论中店铺的地理位置，找到了水军用户和普通用户中地理位置特征分布的差异，并提出了一个基于隐马尔可夫模型HMM(Hidden Markov Model)的\emph{SpamTracer}模型用于分辨水军用户和正常用户。我们的实验结果展示了SpamTracer可以在不平衡的数据集中达到71\%的准确率（(Accuracy)和76\%的召回率(Recall)。这个结果在稳定性上超过一些优秀的经典方法。此外，SpamTracer可以帮助我们分析人工水军的行动规律。这些规律反映了商家们倾向于在合适何地雇佣人工水军来增加收入。我们还发现了一小部分人工水军倾向于和在一个小商圈内的多个商家达成合作关系。

\keywords{\large O2O商务平台， 水军检测， 地理位置， 隐马尔可夫模型}
\end{abstract}

\begin{englishabstract}

Nowadays, O2O(Online To Offline) commercial platforms are playing a crucial role in our daily purchases. However, some people are trying to manipulate the online market maliciously by opinion spamming, a kind of web fraud behavior like writing fake reviews, due to fame and profits, which will harm online purchasing environment and should be detected and eliminated. Moreover, manual spammers are more deceptive compared with old web spambots. Several sophisticated and efficient methods have been proposed in spamming review detection field. However, geolocation was neglected in almost all those acknowledged works. Our investigation presented that geolocation can well reflect the distinctions between spammers and normal users. In this research, we analyzed the geolocations of shops in review, found the distinct distribution features of those in spamming and non-spamming users, and proposed a \emph{SpamTracer} model that can identify spammers and non-spammers by exploiting an improved HMM(Hidden Markov Model). Our experiment demonstrated that SpamTracer could achieve 71\% accuracy and 76\% recall in the unbalanced dataset, outperforming some excellent classical approaches in the aspect of stability. Furthermore, SpamTracer can help to analyze the regularities of spamming actions. Those regularities reflect the time and location in which online shops are likely to hire spammers to increase their turnover. We also found that a small group of spammers tend to work with plural shops located in a small business zone.

\englishkeywords{\large O2O Commercial Platform, Spamming Detection, Geolocation, Hidden Markov Model}
\end{englishabstract}

